Dark Control:\\ Towards a Unified Account of Default Mode Function\\ by Markov Decision Processes

### 2017-12-06 paper/paper.tex
fix affiliations
Danilo's changes for R1

\maketitle
\small{
    \textbf{1} Universit\'e Paris-Saclay, INRIA, Parietal Team, Saclay, France\\
    \textbf{2} Universit\'e Paris-Saclay, CEA, Neurospin, Gif-sur-Yvette, France\\
    \textbf{3} Department of Psychiatry, Psychotherapy and Psychosomatics, RWTH Aachen University, Aachen, Germany\\
    \textbf{4} Institut Pasteur, Human Genetics and Cognitive Functions Unit, Paris, France\\
    \textbf{5} CNRS UMR 3571 Genes, Synapses and Cognition, Institut Pasteur, Paris, France\\
    \textbf{6} University Paris Diderot, Sorbonne Paris Cit\'e, Paris, France\\
    \textbf{7} Centre de Bioinformatique, Biostatistique et Biologie Int\'egrative, Paris, France
}

\begin{abstract}
The Default Mode Network (DMN) is believed to subserve the
baseline mental activity in humans.
%
Its highest energy consumption compared to other brain networks and
its intimate coupling with conscious awareness are both pointing to
an overarching function.
%
Many research streams support an evolutionarily adaptive role in
envisioning experience to anticipate the future.
In the present work, we propose a \textit{process model}
that tries to explain \textit{how}
the DMN may implement
continuous evaluation and prediction of the environment to guide behavior.
%
DMN function is recast in terms of
control theory and reinforcement learning by basing it on Markov decision processes.
%
We argue that our formal account of DMN function naturally accommodates as special cases
the previously proposed cognitive accounts on
(1) predictive coding,
(2) semantic associations, and
(3) a ``sentinel'' role.
%
Moreover, this process model for the neural optimization of complex behavior in the DMN
offers parsimonious explanations for
recent experimental findings in animals and humans.
\end{abstract}

@@

The present work adopts the perspective of
a human \textit{agent} faced with the choice of the next actions
and guided by outcomes
of really happened, hypothetically imagined, and
expected futures to optimize behavioral performance.
Formally, a particularly attractive framework
to describe, quantify, and predict intelligent systems, such as the brain,
is proposed to be the combination of control theory and
reinforcement learning (RL).
An intelligent agent improves the interaction with the environment
by continuously updating its computation of value estimates and action predispositions
through integration of feedback outcomes.
Henceforth,
\textit{control} refers to the influence that an agent exerts when interacting
with the environment to reach preferred states.

@@

We argue that DMN implication in many
advanced cognitive processes in humans
can be recast as prediction error minimization
based on probabilistic mental simulations,
thus maximizing action outcome across multiple time scales.
Such a purposeful optimization objective
may be solved by a stochastic approximation
based on a brain implementation of Markov Chain Monte Carlo (MCMC) sampling
\citep{tenenbaum2011grow}.
Even necessarily imperfect memory recall,
random day-time mind-wandering, and
seemingly arbitrary dreams during sleep
may provide blocks of pseudo-experience to iteratively
optimize the behavior of the organism.

@@

\paragraph*{Towards Model-free reinforcement learning for the DMN.}
Model-free RL can be plausibly realized in the human brain \citep{doherty2015structure}. Indeed,
it has been proposed \citep{gershman2015computational} that a core property of human intelligence  underlie improvement
of expected utility outcomes as a strategy for action choice in uncertain
environments, a situation perfectly captured by the formalism of MDPs.
It has also long been proposed \citep{dayan2008decision} that there
is a rather direct mapping of model-free RL learning algorithms
onto aspects of the brain.
The neurotransmitter dopamine could serve
as a ``teaching signal'' to better estimate value associations
and action policies by controlling
synaptic plasticity in the reward-processing circuitry, including the NAc.
In contrast, \textit{model-based RL} would start off with some mechanistic assumptions about the dynamics of the world.
These can be assumptions about the physical laws governing the agent's environment or constraints on the state space, transition probabilities between states,
reward contingencies, etc.
% For instance, if a rat in a maze knows
% that standing still will produce no change in the environment, and in particular will not eventually lead to finding the food.
An agent might represent such knowledge about the world as follows:
\begin{itemize}
\item $r(s, \text{``stand still''}) = 0$ if $s$ does not correspond to a location
offering relevant resources.
\item $p(s'|s,\text{``stand still''}) = 1$ if $s'=s$ and $0$ otherwise.
\item etc.
\end{itemize}
% Model-based assumes knowledge of the environment in terms of the transition probabilities between states, the reward contingencies for state-action pairs, or any form of representation of the environment.
Such knowledge can of course be partly learned from the environment: the agent learns a model for the world alongside learning to make optimal decisions using this model. These methods learn what the effect is going to be of taking an particular action in a particular state. The result is an estimate of the underlying MDP which can then be either solved exactly or approximately, depending on the setting and what is feasible. The main problem then is to "connect the dots", by using dynamic programming --for example.

@@

\begin{mdframed}
% neuroscience of Bellman equation
  \vspace{2em}
  \textbf{Box 1: Neural correlates of the Bellman equation in the DMN}
% \hspace{-1.5em}
Relating decomposition of consecutive action choices by the Bellman equation
to neuroscience,
specific neural activity in the dorsal prefrontal cortex (BA9)
was linked to processing ``goal-tree sequences''
in human neuroimaging experiments
\citep{koechlin1999role, koechlin2000dissociating}.
Sub-goal exploration may require multi-task switching
between cognitive processes
as later parts of a solution
frequently depend on respective earlier steps in a given solution path, which
necessitates storage of expected intermediate outcomes.
As such,
``cognitive branching'' operations for nested processing of behavioral strategies
are likely to
entail secondary reallocation of attention and working-memory resources.
Further neuroimaging experiments \citep{braver2002role} corroborated
the prefrontal DMN to subserve
``processes related to the management and monitoring of sub-goals while maintaining information in working memory''.
%
Moreover,
neurological patients with lesions in this DMN region were reported
to be impaired in aspects of realizing ``multiple sub-goal scheduling''
\citep{burgess2000cognitive}.
Hence,
the various advanced human mental abilities subserved by the DMN, such as
planning and abstract reasoning, can be viewed to involve some form of
action-decision branching to enable higher-order executive control.
\end{mdframed}

@@

\subsubsection{Does the hippocampus subserve MCMC sampling?}
In RL, MCMC simulation is a common means to update the agent's belief state.
% \citep{silver2010monte}.
MCMC simulation provides a simple method for evaluating the value of a state.
They provide an effective mechanism both for tree search (of the considered
action trajectories)
and for belief state updates, breaking the curse of dimensionality and allowing much greater scalability than an RL agent without stochastic resampling procedures.
Such methods have scaling as a function of available data (i.e., sample complexity) that
is determined only by the underlying difficulty of the MDP, rather than the size of the state space or observation space,
which can be prohibitively large.

In the human brain,
the HC could contribute to synthesizing imagined sequences of world states,
actions and rewards \citep{aronov2017, chao2017interaction, boyer2008evolutionary}.
These simulations of experience batches
would be used to update the value function, without ever looking inside the black box describing the model's dynamics \citep{lavilleon2015}.
This would be a simple control algorithm by evaluating all legal actions and selecting the action with
highest expected cumulative rewards.
In MDPs, MCMC simulation provides an effective mechanism both for tree search and for belief-based state updates, breaking the curse of dimensionality and allowing much greater scalability than has previously been possible \citep{silver2016mastering}.
% Much recent work points to MCMC or stochastic sampling-based approximations as a unifying framework for understanding how Bayesian inference may work practically across all these levels, in minds, brains, and machines. \textbf{XXX elvis: refs needed in last sentence. Plus, should be really bring up Bayesian?}

@@

\subsection{Putting everything together}
The DMN is today known to consistently increase in neural
  activity when humans engage in cognitive processes that are detached from
  the current sensory environment. Additionally,
  this network was proposed to be situated
  at the top of the brain network hierarchy, with
  the subordinate salience and dorsal attention network in the middle and
  the unimodal sensory cortices at the bottom
  \citep{carhart2010default, margulies2016situating}.
  Its putative involvement in thinking about the past,
  hypothetical experiences, and the future
  appears to tie in with the implicit computation of
  action and state cascades as a function of what happened in the past.
  A policy matrix encapsulates the repertoire of possible actions
    on the world given a current state.
    The policy matrix encodes the probabilites of
    choosing actions to be executed in a certain situation.
The DMN may subserve
  constant exploration of possible action trajectories and
  nested estimaton of their
  cumulative reward outcomes. Implicit computation of future choices
  provides an explanation for the
  evolutionary emergence and practical usefulness of
  mind-wandering at day-time and dreams during sleep
  in humans.
\begin{figure}[!h]
  \includegraphics[width=.9\linewidth]{neurobiological_and_rl_overview_DMN.pdf}
  \caption{\textbf{Default mode network:
  neurobiological implementation of reinforcement learning.}
  Overview of how the constituent nodes of the DMN (refer to section \ref{sec:nodes}) may
  map onto computational components necessary for an RL agent.}
  \label{fig:rl_process_chart}
\end{figure}

The HC may contribute to generation of
perturbed action-transition-state-reward samples
as batches of pseudo-experience
(i.e., imagined, hypothesized, and recalled mental scenarios).
The small variations in these experience samplings allow searching
a larger space of model parameters and possible experiences.
Taken to its extreme, stochastic recombination of experience
building blocks can further optimize the behavior of the RL agent
by model learning from scenarios in the environment that the agent might
only very rarely or never encounter.
An explanation is thus offered for experiencing seemingly familiar situations that
a human has however never actually encountered (i.e., d\'{e}j\`{a} vu effect).
While such a situation may not have been experienced in the physical world,
the DMN may have previously stochastically generated, evaluated, and adapted to
such a randomly synthesized situation.
In the absence of environmental input and feedback
(e.g., mind-wandering or sleep),
mental scene construction allows for pseudo-experiencing possible
future scenarios and action outcomes.
Our formal account of DMN function
thus acknowledges the unavoidable stochasticity of
computation in neural systems \citep{faisal2008noise}.

@@

\subsection{Semantic hypothesis}
Another frequently proposed cognitive account to explain DMN function revolves
around forming logical associations and abstract analogies between
experiences and conceptual knowledge derived from past behavior
\citep{bar2007proactive, binder1999conceptual, constantinescu2016organizing}.
Analogies might naturally tie incoming new sensory stimuli to
explicit world knowledge (i.e., semantics)
\citep{bar2009proactive}.
The encoding of complex environmental features could thus be facilitated
by association to known similar states.
%
Going beyond isolated meaning and concepts extracted from the world,
semantic building blocks may need to get recombined to enable
mental imagery of non-existing scenarios.
As such, semantic knowledge would be a prerequisite for optimizing behavior
by constantly simulating possible future scenarios
\citep{boyer2008evolutionary, binder2011neurobiology}.
Such cognitive processes can afford
the internal construction and elaboration of necessary information
that is not presented in the surrounding sensory environment
by recombining building blocks of
concept knowledge and episodic memories
\citep{hassabis2009construction}.
Indeed, in aging humans, remembering the past and imagining the future
equally decreased in the level of detail and were associated with
concurrent deficits in forming and integrating relationships between
items \citep{addis2008age, spreng2006temporal}.
Further,
% a constructive account can explain the reciprocal relationship
% between an egocentric first person perspective and
% an allocentric bird’s eye perspective immersed in
% self-reflection, semantic associations, and autobiographical memories.
% %
% Cognitive aspects of egocentric-allocentric switching
episodic memory, language, problem solving,
planning, estimating others' thoughts, and spatial navigation
represent neural processes that are likely to
build on abstract world knowledge and logical associations
for integrating the constituent elements in rich and coherent mental scenes
\citep{schacter2007remembering}.
Such scene construction processes could contribute to interpreting the
present and foretelling the future.
Further,
mental scene construction has been proposed
to imply a distinction between
engagement in the sensory environment
and internally generated mind-wandering
\citep{buckner2007self}.
These investigators stated that
``A computational model [...] will probably require a form of
regulation by which perception of the current world is suppressed
while simulation of possible alternatives are constructed,
followed by a return to perception of the present.''.
% The semantic hypothesis is for instance supported by evidence in animals that
% could learn a \textit{cognitive map of the environment}
% and exploit it later for other means \citep{tolman1948cognitive}.

>>>>

\maketitle
\small{
    \textbf{1} INRIA, Parietal Team, Saclay, France\\
    \textbf{2} Neurospin, CEA, Gif-sur-Yvette, France\\
    \textbf{3} Department of Psychiatry, Psychotherapy and Psychosomatics, RWTH Aachen University, Aachen, Germany\\
    \textbf{4} Institut Pasteur, Human Genetics and Cognitive Functions Unit, Paris, France\\
    \textbf{5} CNRS UMR 3571 Genes, Synapses and Cognition, Institut Pasteur, Paris, France\\
    \textbf{6} University Paris Diderot, Sorbonne Paris Cit\'e, Paris, France\\
    \textbf{7} Centre de Bioinformatique, Biostatistique et Biologie Int\'egrative, Paris, France
}

\begin{abstract}
The Default Mode Network (DMN) is believed to subserve the
baseline mental activity in humans.
%
Its highest energy consumption compared to other brain networks and
its intimate coupling with conscious awareness are both pointing to
an overarching function.
%
Many research streams support an evolutionarily adaptive role in
envisioning experience to anticipate the future.
In the present work, we propose a \textit{process model}
that tries to explain \textit{how}
the DMN may implement
continuous evaluation and prediction of the environment to guide behavior.
%
% DMN function is recast in terms of
% control theory and reinforcement learning by basing it on Markov decision processes.
%
Specifically, we answer the question whether the neurobiological properties of the default mode network collectively provide the computational building blocks necessary for a Markov Decision Process.
%
We argue that our formal account of DMN function naturally accommodates as special cases
the previously proposed cognitive accounts on
(1) predictive coding,
(2) semantic associations, and
(3) a ``sentinel'' role.
%
Moreover, this process model for the neural optimization of complex behavior in the DMN
offers parsimonious explanations for
recent experimental findings in animals and humans.
\end{abstract}

@@

The present work adopts the perspective of
a human \textit{agent} faced with the choice of the next actions
and guided by outcomes
of really happened, hypothetically imagined, and
expected futures to optimize behavioral performance.
Formally, a particularly attractive framework
to describe, quantify, and predict intelligent systems, such as the brain,
is proposed to be the combination of control theory and
reinforcement learning (RL).
An intelligent agent improves the interaction with the environment
by continuously updating its computation of value estimates and action predispositions
through integration of feedback outcomes.
That is, ``[agents], with their actions, modify the environment and in doing so partially determine their next stimuli, in particular stimuli that are necessary for triggering the next action''
\citep{pezzulo2011grounding}.
Agents with other behavioral policies therefore sample different
distributions of action-perception trajectories \citep{ghavamzadeh2015bayesian}.
Henceforth,
\textit{control} refers to the influence that an agent exerts when interacting
with the environment to reach preferred states.

@@

We argue that DMN implication in many
advanced cognitive processes in humans
can be recast as prediction error minimization
based on probabilistic mental simulations
- ``covert forms of action and perception'' \citep{pezzulo2011grounding} -,
thus maximizing action outcome across multiple time scales.
Such a purposeful optimization objective
may be solved by a stochastic approximation
based on a brain implementation of Markov Chain Monte Carlo (MCMC) sampling
\citep{tenenbaum2011grow}.
Even necessarily imperfect memory recall,
random day-time mind-wandering, and
seemingly arbitrary dreams during sleep
may provide blocks of pseudo-experience to iteratively
optimize the behavior of the organism.

@@

\paragraph*{Towards Model-free reinforcement learning for the DMN.}
Model-free RL can be plausibly realized in the human brain \citep{doherty2015structure, daw2014algorithmic}.
Indeed,
it has been proposed \citep{gershman2015computational} that a core property of human intelligence  underlie improvement
of expected utility outcomes as a strategy for action choice in uncertain
environments, a situation perfectly captured by the formalism of MDPs.
It has also long been proposed \citep{dayan2008decision} that there
is a rather direct mapping of model-free RL learning algorithms
onto aspects of the brain.
The neurotransmitter dopamine could serve
as a ``teaching signal'' to better estimate value associations
and action policies by controlling
synaptic plasticity in the reward-processing circuitry, including the NAc.
In contrast, \textit{model-based RL} would start off with some mechanistic assumptions about the dynamics of the world.
These can be assumptions about the physical laws governing the agent's environment or constraints on the state space, transition probabilities between states,
reward contingencies, etc.
% For instance, if a rat in a maze knows
% that standing still will produce no change in the environment, and in particular will not eventually lead to finding the food.
An agent might represent such knowledge about the world as follows:
\begin{itemize}
\item $r(s, \text{``stand still''}) = 0$ if $s$ does not correspond to a location
offering relevant resources.
\item $p(s'|s,\text{``stand still''}) = 1$ if $s'=s$ and $0$ otherwise.
\item etc.
\end{itemize}
% Model-based assumes knowledge of the environment in terms of the transition probabilities between states, the reward contingencies for state-action pairs, or any form of representation of the environment.
Such knowledge can of course be partly learned from the environment: the agent learns a model for the world alongside learning to make optimal decisions using this model. These methods learn what the effect is going to be of taking an particular action in a particular state. The result is an estimate of the underlying MDP which can then be either solved exactly or approximately, depending on the setting and what is feasible. The main problem then is to "connect the dots", by using dynamic programming --for example.

@@

\begin{mdframed}
% neuroscience of Bellman equation
  \vspace{2em}
  \textbf{Box 1: Neural correlates of the Bellman equation in the DMN}
% \hspace{-1.5em}
Relating decomposition of consecutive action choices by the Bellman equation
to neuroscience,
specific neural activity in the dorsal prefrontal cortex (BA9)
was linked to processing ``goal-tree sequences''
in human neuroimaging experiments
\citep{koechlin1999role, koechlin2000dissociating}.
Sub-goal exploration may require multi-task switching
between cognitive processes
as later parts of a solution
frequently depend on respective earlier steps in a given solution path, which
necessitates storage of expected intermediate outcomes.
As such,
``cognitive branching'' operations for nested processing of behavioral strategies
are likely to
entail secondary reallocation of attention and working-memory resources.
Further neuroimaging experiments corroborated
the prefrontal DMN to subserve
``processes related to the management and monitoring of sub-goals while
maintaining information in working memory''
\citep{braver2002role}
and to functionally couple with the hippocampus conditioned by ``deep versus shallow planning''
\citep{kaplan2017neural}.
%
Moreover,
neurological patients with lesions in this DMN region were reported
to be impaired in aspects of realizing ``multiple sub-goal scheduling''
\citep{burgess2000cognitive}.
Hence,
the various advanced human mental abilities subserved by the DMN, such as
planning and abstract reasoning, can be viewed to involve some form of
action-decision branching to enable higher-order executive control.
\end{mdframed}

@@

\subsubsection{Does the hippocampus subserve MCMC sampling?}
In RL, MCMC simulation is a common means to update the agent's belief state
by stochastic sampling around states and possible transitions \citep{daw2014algorithmic}.
% \citep{silver2010monte}.
MCMC simulation provides a simple method for evaluating the value of a state.
They provide an effective mechanism both for tree search (of the considered
action trajectories)
and for belief state updates, breaking the curse of dimensionality and allowing much greater scalability than an RL agent without stochastic resampling procedures.
Such methods have scaling as a function of available data (i.e., sample complexity) that
is determined only by the underlying difficulty of the MDP, rather than the size of the state space or observation space,
which can be prohibitively large.

In the human brain,
the HC could contribute to synthesizing imagined sequences of world states,
actions and rewards \citep{aronov2017, chao2017interaction, boyer2008evolutionary}.
These simulations of experience batches
would be used to update the value function, without ever looking inside the black box describing the model's dynamics \citep{lavilleon2015}.
A neuroimaging experiment in humans for instance identified hippocampal signals that specifically preceded upcoming choice performance in prospective planning in new environments
\citep{kaplan2017neural}.
This would be a simple control algorithm by evaluating all legal actions and selecting the action with
highest expected cumulative rewards.
In MDPs, MCMC simulation provides an effective mechanism both for tree search and for belief-based state updates, breaking the curse of dimensionality and allowing much greater scalability than has previously been possible \citep{silver2016mastering}.
This is because expected consequences of action choices can be well evaluated although only a subset of the states are actually considered \citep{daw2014algorithmic}.
% Much recent work points to MCMC or stochastic sampling-based approximations as a unifying framework for understanding how Bayesian inference may work practically across all these levels, in minds, brains, and machines. \textbf{XXX elvis: refs needed in last sentence. Plus, should be really bring up Bayesian?}

@@

\subsection{Putting everything together}
The DMN is today known to consistently increase in neural
activity when humans engage in cognitive processes that are relatively detached from
the current sensory environment.

The more familiar and predictable the current environment, the more resources remain for allocating DMN activity to MDP processes extending beyond the present time and sensory context. In line with this perspective, DMN engagement was shown to heighten and relate to effective behavioral responses in the practiced phase of a demanding cognitive flexibility task, as compared to acquisition phase when participants learned context-specific rules. This involvement in automated decision-making lead the authors to propose an ``autopilot'' role for the DMN \citep{vatansever2017pnas}, which may contribute to optimizing control of the organism in general. Among all DMN nodes, the RTPJ has probably a most evident role as network-switching relay calibrating between processing of environment-engaged versus internally generated information \citep{downar2000multimodal, golland2006extrinsic, bzdok2013tpj}.

Additionally,
this network was proposed to be situated
at the top of the brain network hierarchy, with
the subordinate salience and dorsal attention network in the middle and
the unimodal sensory cortices at the bottom
\citep{carhart2010default, margulies2016situating}.
Its putative involvement in thinking about the past,
hypothetical experiences, and the future
appears to tie in with the implicit computation of
action and state cascades as a function of what happened in the past.
A policy matrix encapsulates the repertoire of possible actions
on the world given a current state.
The policy matrix encodes the probabilites of
choosing actions to be executed in a certain situation.
The DMN may subserve
  constant exploration of possible action trajectories and
  nested estimaton of their
  cumulative reward outcomes. Implicit computation of future choices
  provides an explanation for the
  evolutionary emergence and practical usefulness of
  mind-wandering at day-time and dreams during sleep
  in humans.
\begin{figure}[!h]
  \includegraphics[width=.9\linewidth]{neurobiological_and_rl_overview_DMN.pdf}
  \caption{\textbf{Default mode network:
  neurobiological implementation of reinforcement learning.}
  Overview of how the constituent nodes of the DMN (refer to section \ref{sec:nodes}) may
  map onto computational components necessary for an RL agent.}
  \label{fig:rl_process_chart}
\end{figure}

The HC may contribute to generation of
perturbed action-transition-state-reward samples
as batches of pseudo-experience
(i.e., imagined, hypothesized, and recalled mental scenarios).
The small variations in these experience samplings allow searching
a larger space of model parameters and possible experiences.
Taken to its extreme, stochastic recombination of experience
building blocks can further optimize the behavior of the RL agent
by model learning from scenarios in the environment that the agent might
only very rarely or never encounter.
An explanation is thus offered for experiencing seemingly familiar situations that
a human has however never actually encountered (i.e., d\'{e}j\`{a} vu effect).
While such a situation may not have been experienced in the physical world,
the DMN may have previously stochastically generated, evaluated, and adapted to
such a randomly synthesized situation.
Generated representations arguably are ``internally manipulable,
and can be used for attempting actions internally,
before or instead of acting in the external reality,
and in diverse goal and sensory contexts, i.e. even outside the context in which they were learned''
\citep{pezzulo2011grounding}.
In the absence of environmental input and feedback
(e.g., mind-wandering or sleep),
mental scene construction allows for pseudo-experiencing possible
future scenarios and action outcomes.
Our formal account of DMN function
thus acknowledges the unavoidable stochasticity of
computation in neural systems \citep{faisal2008noise}.

@@

\subsection{Semantic hypothesis}
Another frequently proposed cognitive account to explain DMN function revolves
around forming logical associations and abstract analogies between
experiences and conceptual knowledge derived from past behavior
\citep{bar2007proactive, binder1999conceptual, constantinescu2016organizing}.
Analogies might naturally tie incoming new sensory stimuli to
explicit world knowledge (i.e., semantics)
\citep{bar2009proactive}.
The encoding of complex environmental features could thus be facilitated
by association to known similar states.
%
Going beyond isolated meaning and concepts extracted from the world,
semantic building blocks may need to get recombined to enable
mental imagery of non-existing scenarios.
As such, semantic knowledge would be a prerequisite for optimizing behavior
by constantly simulating possible future scenarios
\citep{boyer2008evolutionary, binder2011neurobiology}.
Such cognitive processes can afford
the internal construction and elaboration of necessary information
that is not presented in the surrounding sensory environment
by recombining building blocks of
concept knowledge and episodic memories
\citep{hassabis2009construction}.
Indeed, in aging humans, remembering the past and imagining the future
equally decreased in the level of detail and were associated with
concurrent deficits in forming and integrating relationships between
items \citep{addis2008age, spreng2006temporal}.
Further,
% a constructive account can explain the reciprocal relationship
% between an egocentric first person perspective and
% an allocentric bird’s eye perspective immersed in
% self-reflection, semantic associations, and autobiographical memories.
% %
% Cognitive aspects of egocentric-allocentric switching
episodic memory, language, problem solving,
planning, estimating others' thoughts, and spatial navigation
represent neural processes that are likely to
build on abstract world knowledge and logical associations
for integrating the constituent elements in rich and coherent mental scenes
\citep{schacter2007remembering}.
``[P]redictions and simulations are not only automatically elicited by external events but can be endogenously generated when needed. [...] The mechanism of access via simulation could be a widespread method for accessing and producing knowledge, and represents a valid alternative to the traditional idea of storage and retrieval''
\citep{pezzulo2011grounding}.
Such scene construction processes could contribute to interpreting the
present and foretelling the future.
Further,
mental scene construction has been proposed
to imply a distinction between
engagement in the sensory environment
and internally generated mind-wandering
\citep{buckner2007self}.
These investigators stated that
``A computational model [...] will probably require a form of
regulation by which perception of the current world is suppressed
while simulation of possible alternatives are constructed,
followed by a return to perception of the present.''.
% The semantic hypothesis is for instance supported by evidence in animals that
% could learn a \textit{cognitive map of the environment}
% and exploit it later for other means \citep{tolman1948cognitive}.
